Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-25 R0V0.tex
Implement changes proposed on the ReviewHSS20170124

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this paper, input-affine nonlinear systems are considered. The problem is the design of structured (for instance, decentralized or distributed) controllers for this class of systems. Although control-Lyapunov functions are the natural candidate to design feedback laws, in this case, numerical methods employed to construct for these functions usually leads to a non-convex optimization problem. Moreover, it may require to verify the positiveness of a function with, at least, $n^2$ elements. In this paper, control-contraction metrics (CCMs) are employed to design controllers with suitable topological (distributed) structures. By exploiting sparsity, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program. An example illustrates the approach for a network system.
\end{abstract}

@@

\mypara For those systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}. However, by the time that this paper was submitted, systematic methods for the search of a CLF were known only for particular systems within this class (see, for instance, \cite{MazencMalisoff2006}). In addition to the lack of a general systematic approach, the search for a CLF in terms of numerical optimization leads to a problem that is not necessarily convex nor connected \cite{Rantzer:2001}.

\mypara An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs). One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}, due to fact that the \emph{differential / variational} formulation (see definition below) of the system is considered. The obtained controller makes every solution of the closed-loop system exponentially converge to a prescribed solution (see a precise definition below). In contrast to feedback linearization which depends on integrability, the obtained controller depends only on the stabilizability property of the system. This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.

\mypara One of the drawbacks of numerical methods is that, when the system under consideration has a large number of states, it does not scale well. This is due to the fact that the stability verification of a linear system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions). In general, the case is worse, for nonlinear systems.

@@

\mypara For nonlinear systems, the design of structured controllers could be simplified by choosing structured control-Lyapunov functions (see \cite{Dirr2015} and references therein). However, the search for a general control-Lyapunov function is a non-trivial problem by itself (see \cite{MalisoffMazenc2009} for the search of Lyapunov functions). The case can be even worse, when structural constraints are considered.

\mypara For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs satisfying structural constraints, in this work. The systems under consideration are continuously differentiable and affine in the input. One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed, similarly to Lyapunov functions, to measure the exponential convergence of pairs of solutions. Employing CCMs that can be decomposed into the sum of smaller elements, the design of a structured feedback law allowing exponential convergence of solutions is obtained in two steps.

\mypara The first step consists of an off-line computation. The original system is extended with its \emph{differential / variational} formulation. The exponential convergence problem is reformulated in terms of stability of the origin for the extended system. This stability problem is written in terms of a convex optimization problem under the prescribed structural constraint. The solution consists of a pair of matrices: the Riemannian metric and the \emph{differential / variational} feedback law. The second step consists of an on-line optimization. The obtained \emph{differential / variational} controller is integrated along geodesics (see definition below).

\mypara At this point, the three contributions of this work can be highlighted. First, using the methodology for synthesis of CCMs introduced in \cite{Manchester2014a} and imposing a (block-)diagonal structure constraint, a feedback law with prescribed structure is obtained for nonlinear systems. Second, because the CCM has a (block-)diagonal structure, the computation of the online integration phase, which corresponds to an optimization problem, is distributed. Third, when the system is described a non-strongly connected graph, the structure imposed on the CCM allows to reduce the number of equations needed to  verify stability. Note that the proposed method provides an explicit algorithm to design the controller which makes this approach constructive.

@@

\mypara Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$. A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$. Given two nodes $i,j\in\mathscr{V}$, and ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}. A path is said to be \emph{cycle} if no edges are repeated and the nodes $i$ and $j-1$  are distinct. A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them. It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise. A graph is said to be a \emph{tree} if it is connected and does not contain cycles. A \emph{leaf} is a node that is adjacent to only one node.

@@

\mypara In other words, Problem~\ref{problem formulation} states that the controller is decomposed into smaller components. Each of these depends on the states  prescribed by the set $\mathscr{K}$. The definition of the set $\mathscr{K}$ is not restricted to the topology described by the graph $\mathscr{G}$. Given a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ describing the communication network among different controllers, the set $\mathscr{K}$ can be defined as a subset of $\mathscr{V}_c$.

\mypara The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design feedback laws with a prescribed structure (topology). Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\scalebox{0.95}{$\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i\;.
	\end{array}\right.$}
\end{equation}
As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to memory constraints. However, by exploring sparsity, up to 512 of theses systems can be connected and the controller can be computed.

@@

\mypara The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows. Given a fixed two control $u$ for system \eqref{eq:general system}, $\delta_u\equiv0$. If the Euclidean norm of every solution $\Delta_x(t,x,\delta_x,u,0)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially. The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.

@@

\mypara The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions of this system converge to each other exponentially. The proof of this claim, for the case in which $u\equiv0$ and $\delta_u\equiv0$, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.

@@

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control-contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{equation}\label{eq:Artstein-Sontag:inequality}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
		\end{equation}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}. Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides stabilizing a feedback law of the form $\delta_u=K\delta_x$ for system \eqref{eq:general system:differential} defined for every $\delta_x\in\mathbb{R}^n$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.

@@

\mypara Step 1 (Offline MI computation). Consider the change of variables $\eta=M\delta$ and define the matrix $W=M^{-1}$. The set of equations \eqref{eq:Arstein-Sontag} is equivalent (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W=W^\top\succ0$ and a function $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfying the following matrix inequality (MI)
\begin{equation}\label{eq:MI formulation}
	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0\;.
\end{equation}
Note that \eqref{eq:MI formulation} is linear on the matrix variables $W$ and $Y$, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$. Consequently, the MI~\eqref{eq:MI formulation} can be solved with positive semidefinite programming techniques.

@@

\mypara From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints. This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} cannot generally be computed in a distributed manner.

\mypara In this paper, these limitations are addressed by imposing a separable structure over $W$.

@@

\mypara Following the notation introduced in \cite{Tanaka2011}, for each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{align}
		\Xi=&\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |Y_{pq}:\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)\to\mathbb{R},\nonumber\\
		&\mathbin{\mathtt{row}}(Y,p)\in\mathbf{C}(i),\forall p\in\mathbb{N}_{[1,m]},\forall q\in\mathbb{N}_{[1,n]},\nonumber\\
		&i\in\mathbb{N}_{[1,N]}\}\;,
\end{align}
where $Y_{pq}$ is the component of $Y$ located at row $p$ and column $q$, the notation $\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)$ stands for the projection of $\mathbb{R}^n$ onto the subset generated by the components of $x$ indexed by $\mathscr{K}$, $\mathbin{\mathtt{row}}(Y,p)$ is the $p$-th row of $Y$ and $\mathbf{C}$ stands for the subset of $\mathbb{R}^n$ generated by the vector having components zero but those corresponding to the indices defined in $\mathscr{K}$.

@@

\mypara The existence of a control contraction metric for system~\eqref{eq:general system} implies that there exist matrices $(W,Y)$ that are a solution to the MI~\eqref{eq:MI formulation} with structure prescribed by the set $\Xi$.

@@

\mypara 	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
	\begin{equation}\label{eq:K ODE}
		\tfrac{dk^\ast}{ds}(t,s)=K(\gamma(t,s),k^\ast(t,s))\gamma_s(t,s)=:\overline{K}(t,s,k^\ast)\;.
	\end{equation}
	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$. It remains to show that this interval of existence can be extended on $[0,1]$. In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.

@@

	To see how the graph $\mathscr{G}_c$ specifies the set $\Xi$, not that the set of edges $\mathscr{E}_c$ specifies the set $\mathscr{K}$ which, in turn, defines the sets $\mathbf{C}$ and $\mathbin{\mathtt{proj}}_{\mathscr{K}}$. This concludes the proof of Theorem~\ref{thm:main result}.
\end{proof}

\mypara Although Theorem~\ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, the computation of the MI \eqref{eq:MI formulation} not has been said about the parallel compution of the MI~\eqref{eq:MI formulation}. The next section provides sufficient conditions to parallelize the search for a solution to the MI~ \eqref{eq:MI formulation}.

@@

\mypara To that end three methodologies are recalled below: chordal graphs, alternating direction of multipliers (ADMM) and scaled diagonal dominance. The first exploits the network topology to decompose it into smaller complete components. The second method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below). Finally, scaled diagonal dominance exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling. Note that these methodologies can be used either separately or together. The latter would appropriate, when the smaller components of the network have high rank and the computing platform where the solver runs has memory limitations.

\mypara Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.  onsider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denote as $\mathscr{T}(\mathscr{G})$.

\begin{proposition}\label{prop:clique tree decomposition}
	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
\end{proposition}

@@

\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbf{X}(\mathscr{C}_k)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.

@@

\mypara   	Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into the set of matrix inequalities
  	\begin{equation}\label{eq:MIF}
  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]}\;.
	\end{equation}
	This concludes the proof.
\end{proof}

\mypara Note that if a graph is not chordal, it is possible to make it chordal by adding edges to the graph. The obtained graph is said to be a \emph{chordal embedding}. The above procedure can be applied for the chordal embedded graphs.

@@

\mypara Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be relaxed into the following sum-of-squares feasibility program:
\begin{subequations}
\begin{equation}\label{eq:DSOS}
\begin{array}{rcl}
-F_l&\in&\mathbf{SDD}(U_l)\;,
\end{array}
\end{equation}
where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
\begin{equation}
\begin{array}{rcl}
	U_0&=&\ I_h\\
	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
\end{array}
\end{equation}
\end{subequations}
Note that, when the requirement of $A$ is diagonally dominant can be interpreted as the network having a weak coupling.

\mypara The alternating direction method of multipliers (ADMM) provides a framework to compute the block-diagonal matrix $W$ to satisfy the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}. To use this methodology, define the set of (resp. sum-of-squares (SOS)) polynomials $\mathbb{R}[x]$ (resp. $\mathbb{SOS}[x]$), and denote the degree of a polynomial $p\in\mathbb{R}[x]$ as $\deg(p)$.

@@

\mypara Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stabilizability of the origin, for some classes of systems.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this paper, large-scale input-affine nonlinear systems are considered. The problem is the design of distributed controllers for this class of network systems. Although control-Lyapunov functions are the natural candidates to design feedback laws, in this case, numerical methods employed to construct for these functions usually lead to a non-convex optimization problem. Moreover, it may require to verify the positiveness of a function with, at least, $n^2$ elements. In this paper, control-contraction metrics (CCMs) are employed to design controllers with suitable distributed structures. By exploiting sparsity, the number of verifications needed can be made smaller, as the search of CCMs is formulated as a distributed semidefinite program. An example illustrates the approach for a network system.
\end{abstract}

@@

\mypara For systems described by input-affine differential equations,  the existence of a control-Lyapunov function (CLF) satisfying the so-called \emph{small control property} provides a ``universal'' formula for a stabilizing feedback law  \cite{Sontag1983,Sontag1989a}. However, by the time that this paper was submitted, systematic methods for the search of a CLF were known only for particular systems within this class (see, for instance, \cite{MazencMalisoff2006}). In addition to the lack of a general systematic approach, the search for a CLF in terms of numerical optimization leads to a problem that is not necessarily convex nor connected \cite{Rantzer:2001}.

\mypara An alternative to CLFs is provided by the so-called control-contraction metrics (CCMs). One of the main advantages of CCMs over CLFs is that the feedback law is obtained by solving a convex optimization problem \cite{Manchester2014a}.

\mypara One of the drawbacks of numerical methods is that, when the system under consideration has a large number of states, it may require a large memory size. This is due to the fact that the stability verification of a linear system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions). In general, the case is worse, for nonlinear systems.

@@

\mypara For nonlinear systems, the design of structured controllers could be simplified by choosing structured control-Lyapunov functions (see \cite{Dirr2015} and references therein). However, the search for a general control-Lyapunov function is a non-trivial problem by itself (see \cite{MalisoffMazenc2009} for the search of Lyapunov functions). The case can be even worse, when structural constraints are imposed.

\mypara For this reason, the structured design of feedback laws for nonlinear systems is investigated with CCMs satisfying structural constraints. The systems under consideration are continuously differentiable and affine in the input. One of the key elements employed to design these controllers is the concept of a Riemannian metric (see the definition below) which is employed, similarly to Lyapunov functions, to measure the exponential convergence of pairs of solutions. Employing CCMs that can be decomposed into the sum of smaller elements, the design of a structured feedback law allowing exponential convergence of solutions is obtained in two steps.

\mypara The first step consists of an off-line computation. The original system is extended with its \emph{differential / variational} formulation. The exponential convergence problem is reformulated in terms of stability of the origin for the extended system. This stability problem is written in terms of a convex optimization problem under the prescribed structural constraint. The solution consists of a pair of matrices: the Riemannian metric and the \emph{differential / variational} feedback law. The second step consists of an on-line optimization. The obtained \emph{differential / variational} controller is integrated along geodesics (see definition below).  In contrast to feedback linearization which depends on integrability, the obtained controller depends only on the stabilizability property of the system. This stability notion is related to contraction theory (an incremental stability property \cite{Angeli2002,Lohmiller1998,Rueffer2013,Sontag2010,Forni2014}) which can be traced back to the work \cite{Lewis1949}.

\mypara At this point, the three contributions of this work can be highlighted. First, using the methodology for synthesis of CCMs introduced in \cite{Manchester2014a} and imposing a (block-)diagonal structural constraint, a distributed feedback law is obtained. Second, because the CCM has a (block-)diagonal structure, the computation of the online integration phase, which corresponds to an optimization problem, is also distributed. Third, the structure imposed on the CCM allows to reduce the number of equations needed to  verify stability. Note that the proposed method provides an explicit algorithm to design the controller.

@@

\mypara Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$. A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$. Given two nodes $i,j\in\mathscr{V}$, an ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}. A path is said to be \emph{cycle} if no edges are repeated and the nodes $i$ and $j-1$  are distinct. A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them. It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise. A graph is said to be a \emph{tree} if it is connected and does not contain cycles. A \emph{leaf} is a node that is adjacent to only one node.

@@

\mypara In other words, Problem~\ref{problem formulation} states that each component of the controller depends on the states prescribed by the set $\mathscr{K}$. The definition of the set $\mathscr{K}$ is not restricted to the topology described by the graph $\mathscr{G}$, for instance, it can be described by a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ that defined the communication network among different controllers.

\mypara The constraint on the components of $k^\ast$ described in Problem~\ref{problem formulation} is particularly relevant for the design of distributed feedback laws with a prescribed topology (described possibly by $\mathscr{G}_c$). Consider the network composed of systems described by the following equation.
\begin{equation}\label{eq:example}
	\scalebox{0.95}{$\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i\;.
	\end{array}\right.$}
\end{equation}
As explained in Section \ref{sec:Illustration}, when more than five of these systems are connected, the CCM approach was unable to provide unconstrained controller on a standard desktop machine, due to memory constraints. However, by exploring sparsity, up to 512 of theses systems can be connected and the distributed controller can be computed.

@@

\mypara The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows. Given a fixed control $u$ for system \eqref{eq:general system}, $\delta_u\equiv0$. If the Euclidean norm of every solution $\Delta_x(t,x,\delta_x,u,0)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} under the input $u$ converge to each other exponentially. The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.

@@

\mypara The existence a contraction metric for system \eqref{eq:general system} implies that every two solutions to this system converge to each other exponentially. The proof of this claim, for the case in which $u\equiv0$ and $\delta_u\equiv0$, can be found in \cite[Theorem 1]{Lewis1951}, and \cite[Theorems 5.7 and 5.33]{Reich2005}, and \cite[Lemma 3.3]{Isac2008}.

@@

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control-contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{equation}\label{eq:Artstein-Sontag:inequality}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
		\end{equation}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}. Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x,u)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.

@@

\mypara Step 1 (Offline MI computation). Consider the change of variables $\eta=M\delta$ and define the matrix $W=M^{-1}$. The set of equations \eqref{eq:Arstein-Sontag} is equivalent (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) to the existence of a bounded differentiable function $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ such that $W(\cdot)=W(\cdot)^\top\succ0$ and a function $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ satisfying the following matrix inequality (MI)
\begin{equation}\label{eq:MI formulation}
	-\dot{W}+AW+WA^\top+BY+(BY)^\top+2\lambda W\prec0
\end{equation}
uniformly over $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$. Note that \eqref{eq:MI formulation} is linear on the matrix variables $W$ and $Y$, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$. Consequently, the MI~\eqref{eq:MI formulation} can be solved with positive semidefinite programming techniques.

@@

\mypara From the above steps, even if the problem of imposing a particular structure on $Y$ to correspond to the constraints of Problem \ref{problem formulation} was tractable, the integration of the controller would not necessarily satisfy these constraints. This is due to the fact that the solutions to the optimization problem \eqref{eq:geodesic formulation} cannot generally be computed in a distributed manner. In this paper, these limitations are addressed by imposing a separable structure over $W$.

@@

\mypara For each index $i\in\mathbb{N}_{[1,N]}$, define the set 
\begin{align}
		\Xi=&\{Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}\ |Y_{pq}:\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)\to\mathbb{R},\nonumber\\
		&\mathbin{\mathtt{row}}(Y,p)\in\mathbf{C}(i),\forall p\in\mathbb{N}_{[1,m]},\forall q\in\mathbb{N}_{[1,n]},\nonumber\\
		&i\in\mathbb{N}_{[1,N]}\}\;,
\end{align}
where $Y_{pq}$ is the component of $Y$ located at row $p$ and column $q$, the notation $\mathtt{proj}_{\mathscr{K}(i)}(\mathbb{R}^n)$ stands for the projection of $\mathbb{R}^n$ onto the subset generated by the components of $x$ indexed by $\mathscr{K}$, $\mathbin{\mathtt{row}}(Y,p)$ is the $p$-th row of $Y$ and $\mathbf{C}$ stands for the subset of $\mathbb{R}^n$ generated by the vector having all components zero but those corresponding to the indices defined in $\mathscr{K}$.

@@

@@

\mypara 	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
	\begin{equation}\label{eq:K ODE}
		\tfrac{dk^\ast}{ds}(t,s)=K(\gamma(t,s),k^\ast(t,s))\gamma_s(t,s)=:\overline{K}(t,s,k^\ast)\;.
	\end{equation}
which has a unique solution defined on a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$. It remains to show that this interval of existence can be extended on $[0,1]$. In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.

@@

	\mypara To see how the graph $\mathscr{G}_c$ specifies the set $\Xi$, not that the set of edges $\mathscr{E}_c$ specifies the set $\mathscr{K}$ which, in turn, defines the sets $\mathbf{C}$ and $\mathbin{\mathtt{proj}}_{\mathscr{K}}$. This concludes the proof of Theorem~\ref{thm:main result}.
\end{proof}

\mypara Although Theorem~\ref{thm:main result} provides a methodology to design distributed controllers, \emph{a priori}, nothing has been imposed to compute the MI~\eqref{eq:MI formulation} in a distributed manner. The next section provides sufficient conditions to parallelize the search for a solution to the MI~ \eqref{eq:MI formulation}.

@@

\mypara To that end three methodologies are recalled below: chordal graphs, scaled diagonal dominance and alternating direction of multipliers (ADMM). The first exploits the network topology to decompose it into smaller complete components. The second method exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling. Finally, the last method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below). Note that these methodologies can be used either separately or together. The latter would appropriate, when the smaller components of the network still have a large number of states and the computing platform where the solver runs has memory limitations.

\mypara Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}. Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denoted as $\mathscr{T}(\mathscr{G})$.

\begin{proposition}\label{prop:clique tree decomposition}
	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension. Moreover, if each matrix is negative definite, then the MI~\eqref{eq:MI formulation} is satisfied.
\end{proposition}

@@

\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}(\mathscr{C}_k)$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, let the integer $\dim_k$ denote the dimension of the set $\mathbin{\mathtt{proj}}_{\mathscr{C}_k)}(\mathbb{R}^n)$ and define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.

@@

\mypara Consequently, whenever the following matrix inequality holds 
  	\begin{equation}\label{eq:MIF}
  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]},
	\end{equation}
	uniformly over $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI formulation} holds. This concludes the proof.
\end{proof}

\mypara Note that if a graph is not chordal, it is possible to make it chordal by adding edges to the graph. The obtained graph is said to be a \emph{chordal embedded} and the above procedure can be applied for this graph.

@@

\mypara Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be relaxed into the following sum-of-squares feasibility program:
\begin{subequations}
\begin{equation}\label{eq:DSOS}
\begin{array}{rcl}
-F_l&\in&\mathbf{SDD}(U_l)\;,
\end{array}
\end{equation}
where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
\begin{equation}
\begin{array}{rcl}
	U_0&=&\ I_h\\
	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
\end{array}
\end{equation}
\end{subequations}
Note that, the requirement of $A$ to be diagonally dominant can be interpreted as the network having stable agents interconnected with a weak coupling.

\mypara The alternating direction method of multipliers (ADMM) provides a framework to compute the sum-separable control contraction metrics in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}. To use this methodology, define the set of (resp. sum-of-squares (SOS)) polynomials $\mathbb{R}[x]$ (resp. $\mathbb{SOS}[x]$), and denote the degree of a polynomial $p\in\mathbb{R}[x]$ as $\deg(p)$.

@@

\mypara Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stability of the origin, for some classes of systems.
